Supplemental Material for the manuscript `TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults'

### 2023-06-22 supplements/supplements.tex
minor proof-reading edits

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\linenumbers
\usepackage{csquotes}
\usepackage{setspace}
\captionsetup[figure]{font={stretch=1}}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Supplements for the manuscript `TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults'},
  pdfauthor={Julia Prein1, Manuel Bohn1, Steven Kalinke1, \& Daniel B. M. Haun1},
  pdflang={en-EN},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Supplements for the manuscript `TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults'}
\author{Julia Prein\textsuperscript{1}, Manuel Bohn\textsuperscript{1}, Steven Kalinke\textsuperscript{1}, \& Daniel B. M. Haun\textsuperscript{1}}
\date{}

@@

\authornote{

Correspondence concerning this article should be addressed to Julia Prein, Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany. E-mail: \href{mailto:julia_prein@eva.mpg.de}{\nolinkurl{julia\_prein@eva.mpg.de}}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany}

@@

Comparing the performances of children across our two data collection modes, we found that children participating remotely were slightly more precise.
This difference was especially prominent in younger participants in the box version of the task.
It is conceivable that caregivers were especially prone to influence the behavior of younger children.
In the box version, caregivers might have had more opportunities to interfere since they carried out the clicking for their children.
In an exploratory analysis, we coded parental behavior and environmental factors during remote unsupervised testing.
Due to the time consuming nature of hand coding videos frame by frame, we focused on the subsample with the greatest performance difference between data collection modes: the three-year-olds in the box version of the task (n = 16).
We reasoned that if parental interference cannot explain the greatest performance difference in our sample, the effects would be negligible in the remaining sample.
A trial was defined as the time between two eye blinking sounds.
We transcribed all utterances by parents and children and counted the words uttered by each.
We then classified the utterances into several categories: question asked by child, repeated test questions by caregiver, hints towards agents (how many times the caregivers guided the child's attention to the agent), hints towards eyes (how many times the caregivers guided the child's attention to the agent's eyes), verification of choice (how many times the caregiver questioned or double checked the child's response), mentioning of screen (how many times the caregiver verbally guided the child's attention to the screen), pointing to screen (how many times the caregiver pointed towards the screen), positive \& negative feedback, motivational statements, and incomprehensible utterances.
In addition, we coded how many adults and children were present, whether a response click was obviously conducted by the caregiver themselves, and whether children took a break during the trial.
We conducted a model comparison to estimate the effects of parental interference.
Our null model explained the response behavior by age, while including random effects for subject and target position (model notation in \texttt{R:\ correct\ \textasciitilde{}\ age\ +\ symmetricPosition\ +\ (1\ +\ symmetricPosition\ \textbar{}\ subjID)}.

@@

\begin{table}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrrr}
\toprule
Predictor & WAIC & SE\_WAIC & Weight & ELPD\_DIFF & SE\_ELPD\_DIFF\\
\midrule
By trial - \# Verification choice & 255.98 & 15.66 & 0.34 & 0.00 & 0.00\\
By trial - Null model & 256.77 & 15.05 & 0.23 & -0.40 & 1.18\\
By trial - Parental interference index & 257.24 & 15.32 & 0.18 & -0.63 & 0.99\\
By trial - \# Repeated testquestion & 258.57 & 15.25 & 0.09 & -1.30 & 1.23\\
By trial - \# Words uttered by caregiver & 258.88 & 15.37 & 0.08 & -1.45 & 1.13\\
\addlinespace
By trial - \# Hints eyes & 258.88 & 15.35 & 0.08 & -1.45 & 1.21\\
By subject - \# Repeated testquestion & 83.61 & 10.23 & 0.81 & 0.00 & 0.00\\
By subject - Parental interference index & 88.27 & 12.17 & 0.08 & -2.33 & 3.58\\
By subject - Null model & 89.16 & 11.21 & 0.05 & -2.78 & 3.60\\
By subject - \# Verification choice & 89.96 & 12.04 & 0.03 & -3.18 & 4.47\\
\addlinespace
By subject - \# Words uttered by caregiver & 90.56 & 10.70 & 0.02 & -3.48 & 4.23\\
By subject - \# Hints eyes & 93.02 & 11.84 & 0.01 & -4.71 & 3.76\\
\bottomrule
\end{tabular}}
\end{table}

@@

\begin{table}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrrr}
\toprule
Predictor & WAIC & SE\_WAIC & Weight & ELPD\_DIFF & SE\_ELPD\_DIFF\\
\midrule
Age of childcare entry & 571.66 & 28.13 & 0.73 & 0.00 & 0.00\\
Null model & 575.85 & 30.39 & 0.09 & -2.09 & 4.49\\
Sibling variety score (Peterson, 2000) & 577.91 & 29.85 & 0.03 & -3.12 & 4.64\\
\# Children in household aged 0-18 & 578.01 & 29.70 & 0.03 & -3.18 & 4.72\\
Peer exposure index & 578.04 & 30.23 & 0.03 & -3.19 & 4.70\\
\addlinespace
Sibling variety score (Cassidy et al., 2005) & 578.36 & 29.88 & 0.03 & -3.35 & 4.65\\
\# Household members & 578.70 & 30.35 & 0.02 & -3.52 & 4.50\\
\# Children in household aged 1-12 & 578.93 & 30.04 & 0.02 & -3.64 & 4.86\\
Average hours spent in childcare per day & 579.03 & 30.69 & 0.02 & -3.69 & 4.57\\
\bottomrule
\end{tabular}}
\end{table}

Note that we did not find a great difference in WAIC scores between the compared models (see Supplements for WAIC scores and weights). The model estimates were all considerably smaller than estimates of age, study version and data collection, and all 95\% CIs included zero. Nevertheless, a general pattern emerges: exposure to a more variable social environment positively influenced children's gaze understanding. The number of people and, more specifically, children, as well as the more diverse their age, the more likely children were to understand the agent's gaze cue. The only predictor resulting in a negative estimate was the age at which a participant entered childcare, i.e., the later a child entered, the better performance in the task.

@@

We employed the oREV, an Item Response Theory based open receptive vocabulary task for 3 to 8-year-old children (Bohn, Prein, Delikaya, Haun, \& Gagarina, 2022). Similarly to the TANGO, the task was presented as an interactive web application (see Figure \ref{fig:fig5}; live demo \url{https://ccp-odc.eva.mpg.de/orev-demo/}; source code \url{https://github.com/ccp-eva/orev-demo}).

@@

To estimate the effect of gaze understanding on receptive vocabulary, we fitted a GLMM predicting the task performance by the gaze understanding score (scaled), controlling for age: \texttt{cor\_clt\ \textbar{}\ trials(n\_clt)\ \textasciitilde{}\ age\_centered\ +\ mean\_gaze\_centered}). We modelled the number of participant's correct responses using a \texttt{Binomial} distribution.

@@

\begin{table}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrrr}
\toprule
Predictor & WAIC & SE\_WAIC & Weight & ELPD\_DIFF & SE\_ELPD\_DIFF\\
\midrule
Age of childcare entry & 571.66 & 28.13 & 0.73 & 0.00 & 0.00\\
Null model & 575.85 & 30.39 & 0.09 & -2.09 & 4.49\\
Sibling variety score (Peterson, 2000) & 577.91 & 29.85 & 0.03 & -3.12 & 4.64\\
\# Children in household aged 0-18 & 578.01 & 29.70 & 0.03 & -3.18 & 4.72\\
Peer exposure index & 578.04 & 30.23 & 0.03 & -3.19 & 4.70\\
\addlinespace
Sibling variety score (Cassidy et al., 2005) & 578.36 & 29.88 & 0.03 & -3.35 & 4.65\\
\# Household members & 578.70 & 30.35 & 0.02 & -3.52 & 4.50\\
\# Children in household aged 1-12 & 578.93 & 30.04 & 0.02 & -3.64 & 4.86\\
Average hours spent in childcare per day & 579.03 & 30.69 & 0.02 & -3.69 & 4.57\\
\bottomrule
\end{tabular}}
\end{table}

@@

\begin{longtable}{llr}
\toprule
Current Country of Residence & studytype & n\\
\midrule
\endfirsthead
\multicolumn{3}{@{}l}{\textit{(continued)}}\\
\toprule
Current Country of Residence & studytype & n\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
United Kingdom & vali & 47\\
South Africa & vali & 8\\
Portugal & vali & 6\\
Poland & vali & 5\\
Ireland & vali & 5\\
\addlinespace
Italy & vali & 4\\
Spain & vali & 4\\
Netherlands & vali & 4\\
Canada & vali & 2\\
Australia & vali & 2\\
\addlinespace
France & vali & 2\\
Austria & vali & 2\\
Norway & vali & 1\\
DATA EXPIRED & vali & 1\\
Finland & vali & 1\\
\addlinespace
Greece & vali & 1\\
Germany & vali & 1\\
United States & vali & 1\\
Mexico & vali & 1\\
South Africa & reli & 48\\
\addlinespace
United Kingdom & reli & 19\\
United States & reli & 14\\
Portugal & reli & 10\\
Italy & reli & 7\\
Canada & reli & 6\\
\addlinespace
Spain & reli & 5\\
Ireland & reli & 5\\
Poland & reli & 4\\
Greece & reli & 4\\
Netherlands & reli & 3\\
\addlinespace
CONSENT REVOKED & reli & 3\\
Germany & reli & 3\\
Australia & reli & 2\\
France & reli & 2\\
Czech Republic & reli & 2\\
\addlinespace
Hungary & reli & 2\\
Chile & reli & 1\\
Iceland & reli & 1\\
New Zealand & reli & 1\\*
\end{longtable}

@@

\toprule()

@@

@@

\bottomrule()

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-bohn2022orev}{}}%
Bohn, M., Prein, J., Delikaya, B., Haun, D. B. M., \& Gagarina, N. (2022). \emph{{oREV}: An {Item Response Theory} based open receptive vocabulary task for 3 to 8-year-old children}.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\linenumbers
\usepackage{csquotes}
\usepackage{setspace}
\captionsetup[figure]{font={stretch=1}}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Supplemental Material for the manuscript `TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults'},
  pdfauthor={Julia Prein1, Manuel Bohn1,2, Steven Kalinke1, \& Daniel B. M. Haun1},
  pdflang={en-EN},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Supplemental Material for the manuscript `TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults'}
\author{Julia Prein\textsuperscript{1}, Manuel Bohn\textsuperscript{1,2}, Steven Kalinke\textsuperscript{1}, \& Daniel B. M. Haun\textsuperscript{1}}
\date{}

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany\\\textsuperscript{2} Institute of Psychology, Leuphana University Lüneburg, Germany}

@@

Comparing the performances of children across our two data collection modes, we found that children participating remotely were slightly more precise.
This difference was especially prominent in younger participants in the box version of the task.
It is conceivable that caregivers were especially prone to influence the behavior of younger children.
In the box version, caregivers might have had more opportunities to interfere since they carried out the clicking for their children.
In an exploratory analysis, we coded parental behavior and environmental factors during remote unsupervised testing.
Due to the time consuming nature of hand coding videos frame by frame, we focused on the subsample with the greatest performance difference between data collection modes: the three-year-olds in the box version of the task (n = 0).
We reasoned that if parental interference cannot explain the greatest performance difference in our sample, the effects would be negligible in the remaining sample.
A trial was defined as the time between two eye blinking sounds.
We transcribed all utterances by parents and children and counted the words uttered by each.
We then classified the utterances into several categories: question asked by child, repeated test questions by caregiver, hints towards agents (how many times the caregivers guided the child's attention to the agent), hints towards eyes (how many times the caregivers guided the child's attention to the agent's eyes), verification of choice (how many times the caregiver questioned or double checked the child's response), mentioning of screen (how many times the caregiver verbally guided the child's attention to the screen), pointing to screen (how many times the caregiver pointed towards the screen), positive \& negative feedback, motivational statements, and incomprehensible utterances.
In addition, we coded how many adults and children were present, whether a response click was obviously conducted by the caregiver themselves, and whether children took a break during the trial.
We conducted a model comparison to estimate the effects of parental interference.
Our null model explained the response behavior by age, while including random effects for subject and target position (model notation in \texttt{R:\ correct\ \textasciitilde{}\ age\ +\ symmetricPosition\ +\ (1\ +\ symmetricPosition\ \textbar{}\ subjID)}.

@@

\begin{table}[H]
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrrr}
\toprule
Predictor & WAIC & SE\_WAIC & Weight & ELPD\_DIFF & SE\_ELPD\_DIFF\\
\midrule
By trial - Null model & 256.42 & 15.10 & 0.31 & 0.00 & 0.00\\
By trial - \# Verification choice & 256.57 & 15.46 & 0.29 & -0.07 & 1.08\\
By trial - Parental interference index & 258.08 & 15.38 & 0.14 & -0.83 & 0.76\\
By trial - \# Repeated testquestion & 258.83 & 15.25 & 0.09 & -1.20 & 0.61\\
By trial - \# Hints eyes & 258.88 & 15.30 & 0.09 & -1.23 & 0.50\\
\addlinespace
By trial - \# Words uttered by caregiver & 259.15 & 15.39 & 0.08 & -1.37 & 0.36\\
By subject - \# Repeated testquestion & 83.45 & 10.20 & 0.82 & 0.00 & 0.00\\
By subject - Parental interference index & 88.17 & 12.15 & 0.08 & -2.36 & 3.55\\
By subject - Null model & 89.36 & 11.28 & 0.04 & -2.96 & 3.59\\
By subject - \# Verification choice & 89.94 & 12.01 & 0.03 & -3.25 & 4.44\\
\addlinespace
By subject - \# Words uttered by caregiver & 90.50 & 10.62 & 0.02 & -3.52 & 4.19\\
By subject - \# Hints eyes & 93.02 & 11.84 & 0.01 & -4.78 & 3.71\\
\bottomrule
\end{tabular}}
\end{table}

@@

\begin{table}[H]
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrrr}
\toprule
Predictor & WAIC & SE\_WAIC & Weight & ELPD\_DIFF & SE\_ELPD\_DIFF\\
\midrule
Age of childcare entry & 571.54 & 28.09 & 0.72 & 0.00 & 0.00\\
Null model & 575.80 & 30.43 & 0.09 & -2.13 & 4.51\\
\# Children in household aged 0-18 & 577.29 & 29.61 & 0.04 & -2.88 & 4.70\\
Peer exposure index & 577.90 & 30.20 & 0.03 & -3.18 & 4.65\\
\# Children in household aged 1-12 & 578.02 & 29.93 & 0.03 & -3.24 & 4.69\\
\addlinespace
Sibling variety score (Cassidy et al., 2005) & 578.15 & 29.85 & 0.03 & -3.31 & 4.66\\
Sibling variety score (Peterson, 2000) & 578.21 & 29.84 & 0.03 & -3.34 & 4.64\\
\# Household members & 578.30 & 30.32 & 0.02 & -3.38 & 4.48\\
Average hours spent in childcare per day & 579.04 & 30.66 & 0.02 & -3.75 & 4.56\\
\bottomrule
\end{tabular}}
\end{table}

Note that we did not find a great difference in WAIC scores between the compared models (see Supplements for WAIC scores and weights). The model estimates were all considerably smaller than estimates of age, study version and data collection, and all 95\% CIs included zero. Nevertheless, a general pattern emerges: exposure to a more variable social environment positively influenced children's gaze understanding. The number of people and, more specifically, children, as well as the more diverse their age, the more likely children were to understand the agent's gaze cue. The only predictor resulting in a negative estimate was the age at which a participant entered childcare, i.e., the later a child entered, the better performance in the task. Effect sizes were probably influenced by the lack of variance in the predictors: variables like household size and number of siblings typically vary very little among German households (see distribution characteristics of predictor variables below).

\begin{table}[H]
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrrrrrr}
\toprule
  & n & mean & sd & min & max & skew & kurtosis & se\\
\midrule
Age of childcare entry in months & 109 & 14.96 & 5.54 & 1.0 & 40 & 1.72 & 5.65 & 0.53\\
Average hours spent in childcare per day & 109 & 7.50 & 0.92 & 3.5 & 9 & -0.67 & 1.92 & 0.09\\
\# Household members & 109 & 3.72 & 0.92 & 2.0 & 7 & 0.30 & 0.49 & 0.09\\
\# Children in household aged 0-18 & 109 & 0.83 & 0.79 & 0.0 & 4 & 0.87 & 1.09 & 0.08\\
\# Children in household aged 1-12 & 109 & 0.69 & 0.74 & 0.0 & 4 & 1.23 & 2.67 & 0.07\\
\addlinespace
Sibling variety score (Peterson, 2000) & 109 & 0.60 & 0.56 & 0.0 & 2 & 0.23 & -0.87 & 0.05\\
Sibling variety score (Cassidy et al., 2005) & 109 & 0.63 & 0.54 & 0.0 & 2 & 0.18 & -0.70 & 0.05\\
\bottomrule
\end{tabular}}
\end{table}

@@

We employed the oREV, an Item Response Theory based open receptive vocabulary task for 3 to 8-year-old children (Bohn et al., 2022). Similarly to the TANGO, the task was presented as an interactive web application (see Figure \ref{fig:fig5}; live demo \url{https://ccp-odc.eva.mpg.de/orev-demo/}; source code \url{https://github.com/ccp-eva/orev-demo}).

@@

To estimate the effect of gaze understanding on receptive vocabulary, we fitted a GLMM predicting the task performance by the gaze understanding score (scaled), controlling for age: \texttt{cor\_clt\ \textbar{}\ trials(n\_clt)\ \textasciitilde{}\ age\_centered\ +\ mean\_gaze\_centered}). We modelled the number of participant's correct responses using a \texttt{Binomial} distribution.
In order to combine data of our two TANGO study versions, we transformed continuous click responses from the hedge version into a discrete outcome. After this transformation, we calculated a ``TANGO score'' as the proportion of correctly located targets. See Analysis section of Social-environmental factors for further detail.

@@

\begin{table}[H]
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrrr}
\toprule
Predictor & WAIC & SE\_WAIC & Weight & ELPD\_DIFF & SE\_ELPD\_DIFF\\
\midrule
Age (scaled), TANGO score (scaled) & 570.16 & 26.38 & 0.98 & 0.00 & 0.00\\
Age (scaled) & 577.66 & 27.16 & 0.02 & -3.75 & 4.16\\
Null model & 635.72 & 28.70 & 0.00 & -32.78 & 10.62\\
\bottomrule
\end{tabular}}
\end{table}

{\centering \includegraphics[width=1\linewidth]{../figures/tango_supplements_orev_byagegroup}

\caption{\textbf{Effect of gaze understanding on receptive vocabulary by age group}. Regression lines with 95\% CI show smooth conditional mean based on a linear model (generalized linear model for box version), with \emph{Pearson}'s correlation coefficient \emph{r}. Diamonds show the performance for each subject. The color of data points denotes age group.}\label{fig:fig6}
\end{figure}

@@

\begin{longtable}{llr}
\toprule
currentResidence & studytype & n\\
\midrule
\endfirsthead
\multicolumn{3}{@{}l}{\textit{(continued)}}\\
\toprule
currentResidence & studytype & n\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
United Kingdom & vali & 47\\
South Africa & vali & 8\\
Portugal & vali & 6\\
Poland & vali & 5\\
Ireland & vali & 5\\
\addlinespace
Italy & vali & 4\\
Spain & vali & 4\\
Netherlands & vali & 4\\
Canada & vali & 2\\
Australia & vali & 2\\
\addlinespace
France & vali & 2\\
Austria & vali & 2\\
Norway & vali & 1\\
DATA EXPIRED & vali & 1\\
Finland & vali & 1\\
\addlinespace
Greece & vali & 1\\
Germany & vali & 1\\
United States & vali & 1\\
Mexico & vali & 1\\
South Africa & vali2 & 20\\
\addlinespace
Portugal & vali2 & 11\\
United Kingdom & vali2 & 5\\
France & vali2 & 3\\
Italy & vali2 & 2\\
Spain & vali2 & 2\\
\addlinespace
Poland & vali2 & 2\\
DATA EXPIRED & vali2 & 1\\
Finland & vali2 & 1\\
Czech Republic & vali2 & 1\\
Latvia & vali2 & 1\\
\addlinespace
Switzerland & vali2 & 1\\
South Africa & reli & 48\\
United Kingdom & reli & 19\\
United States & reli & 14\\
Portugal & reli & 10\\
\addlinespace
Italy & reli & 7\\
Canada & reli & 6\\
Spain & reli & 5\\
Ireland & reli & 5\\
Poland & reli & 4\\
\addlinespace
Greece & reli & 4\\
Netherlands & reli & 3\\
CONSENT REVOKED & reli & 3\\
Germany & reli & 3\\
Australia & reli & 2\\
\addlinespace
France & reli & 2\\
Czech Republic & reli & 2\\
Hungary & reli & 2\\
Chile & reli & 1\\
Iceland & reli & 1\\
\addlinespace
New Zealand & reli & 1\\*
\end{longtable}

@@

\toprule\noalign{}

@@

\bottomrule\noalign{}
\endlastfoot

@@

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-bohn2022orev}{}}%
Bohn, M., Prein, J. C., Koch, T., Bee, R. M., Delikaya, B., Haun, D. B. M., \& Gagarina, N. (2022). \emph{{oREV}: An {Item Response Theory} based open receptive vocabulary task for 3 to 8-year-old children} {[}Preprint{]}. {PsyArXiv}. \url{https://doi.org/10.31234/osf.io/4z86w}
